---
title: "ggplot_hook"
author: "Yousuf"
date: "2023-01-23"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

## Setting up my environment

Notes: setting up my R environment by loading the 'tidyverse' and 'palmerpenguiens' packages

```{r loading packages}
library(tidyverse)
library(palmerpenguins)

```
## Visualizations
Here we will go through a series of visualizations
 
### Flipper and body mass in purple
Here we plot a flipper length against body mass

```{r visualize filpper length and body mass in purple, warning=FALSE}
ggplot(data = penguins,aes(x=flipper_length_mm,y=body_mass_g))+
 geom_point(color="Purple")
```


### Flipper and body mass by species
Here we plot a flipper length against body mass
```{r species, warning=FALSE}
ggplot(data = penguins,aes(x=flipper_length_mm,y=body_mass_g))+
  geom_point(aes(shape=species))

```

### Flipper and body mass by species and sex
Here we plot a flipper length against body mass

```{r species and sex, warning=FALSE}
ggplot(data = penguins,aes(x=flipper_length_mm,y=body_mass_g))+ 
  geom_point(aes(color=species, shape=species))+
  facet_wrap(~sex)
```

